\documentclass{pasa}

\title[Kuzushiji Recognition]{Kuzushiji Recognition \\ \large Cognitive Services 2018-19 project report}

\author[Matteo Rizzo, Alessandro Zangari]{\textbf{Matteo Rizzo} - id. 1206694\\ \textbf{Alessandro Zangari} - id. 1207247\\}%
\date{September 2019}

% UNCOMMENT THE LINES BELOW IF YOU WISH TO USE BIBTEX
%Citations may be made using the natbib commands \citet{},\citep{} etc.
\usepackage[authoryear]{natbib}
\bibpunct{(}{)}{;}{a}{}{,}
\setlength{\bibsep}{0.3mm}

\usepackage{aas_macros}
\usepackage{hyperref} 
\hypersetup{colorlinks,citecolor=blue,linkcolor=blue,urlcolor=blue}
\usepackage{graphicx}
\graphicspath{{images/}}
\begin{document}


\input{sections/abstract}

\maketitle

% --- INTRODUCTION ---

\input{sections/introduction}

% --- RELATED WORK ---

\input{sections/related_work}

% --- APPROACHES ---

\input{sections/approaches}

% --- DATASET ---

\input{sections/dataset}

% --- METHOD ---

\input{sections/method}

% --- EXPERIMENTS ---

\input{sections/experiments}

% --- CONCLUSION ---

\input{sections/conclusion}

% --- BIBLIOGRAPHY ---

\input{sections/bibliography}

But in a larger sense we can not dedicate -- we can not consecrate -- we can not hallow this ground. The brave men, living and dead, who struggled, here, have consecrated it far above our poor power to add or detract. The world will little note, nor long remember, what we say here, but can never forget what they did here. It is for us, the living, rather to be dedicated here to the unfinished work which they have, thus far, so nobly carried on \cite{abt1961}. It is rather for us to be here dedicated to the great task remaining before us  that from these honoured dead we take increased devotion to that cause for which they here gave the last full measure of devotion  that we here highly resolve that these dead shall not have died in vain; that this nation shall have a new birth of freedom; and that this government \cite{abt1961} of the people, by the people, for the people, shall not perish from the earth.

\begin{table}
\caption{This is an example of table caption.}
\begin{center}
\begin{tabular}{@{}cc@{}}
\hline\hline
Dimension & Classification accuracy \\
\hline%
 1  & 0.6232 \\
 2  & 0.9635 \\ 
 3  & 0.9724 \\ 
 4  & 0.9690 \\ 
 5  & 0.9840 \\ 
 6  & 0.9842 \\ 
 7  & 0.9873 \\ 
 8  & 0.9884 \\
 9  & 0.9873 \\ 
 10 & 0.9898 \\ 
 11 & 0.9914 \\
\hline\hline
\end{tabular}
\end{center}
\label{tab1}
\end{table}

 
\section{THIS IS AN EXAMPLE OF HEAD LEVEL 1}


\begin{equation}\label{GEV}
\max\limits_{x}\{x^TAx-\rho \|x\|_0: x^TBx\leq 1\},
\end{equation}


\begin{eqnarray*}
	g((x,y),(z,w)):&=&\tau\|x\|_2^2-z^T(A+\tau I_n)z\\
	&&+\rho_\epsilon\sum\limits_{i=1}^n\log(\epsilon+w_i)-2(x-z)^T\\
	&&+\rho_\epsilon\sum\limits_{i=1}^n\frac{y_i-w_i}{w_i+\epsilon}
\end{eqnarray*}

\begin{table*}
\caption{It is rather for us to be here dedicated to the great $\alpha^{(1)}$ and $\alpha^{(2)}$ task remaining before us  that from these honoured dead we take increased devotion to that cause for which they here gave the last.} 
\begin{center}
\begin{tabular*}{\textwidth}{@{}c\x c\x c\x c\x c\x c\x c\x c\x c\x c\x c\x c@{}}
\hline \hline
 Layer   & $V_{\rm P0}$   & $V_{\rm S0}$     &  $\epsilon^{(1)}$  &  $\epsilon^{(2)}$ 
         & $\delta^{(1)}$ & $\delta^{(2)}$  &  $\delta^{(3)}$    & $\gamma^{(1)}$ 
         & $\gamma^{(2)}$ & $\alpha^{(1)}$  & $\alpha^{(2)}$ \\
 number  & (km/s)        & (km/s)          & ~                  & ~ 
         & ~             & ~               & ~                  & ~ 
         & ~             & $(^\circ)$       & $(^\circ)$ \\
%
\hline
 1 & 3.5 & 2.0 & 0.20 & -0.05 & 0.00 & -0.20 & -0.05 & 0.20 & ~0.05 & 20 & 10 \\ 
 2 & 2.5 & 1.5 & 0.10 & -0.15 & 0.05 & -0.15 & ~0.00 & 0.10 & -0.05 & 20 & 40 \\ 
 3 & 3.0 & 1.8 & 0.20 & -0.05 & 0.25 & ~0.05 & ~0.20 & 0.15 & ~0.00 & 20 & 70$^a$ \\
\hline \hline
\end{tabular*}\label{tab2}
\end{center}
\tabnote{$^a$This is an example of table footnote}
\tabnote{This is an example of table footnote}
\tabnote{This is an example of table footnote}
\end{table*}


\begin{acknowledgements}
	This is a multiline text of acknowledgments. We are met here on a great battlefield of that war. We have come to dedicate a portion of it as a final resting place for those who here gave their lives that that nation might live.
\end{acknowledgements}


\begin{appendix}

\section{AN EXAMPLE OF APPENDIX HEAD}

 Consider a data set
\begin{equation}
S=(f_{ij})_{m\times n}
\end{equation} the \(i\)th
data point of which is
\[ (f_{i1}, . . . , f_{in}).\]
 Let $\overline{f}_q=\frac{1}{m}\sum_{i=1}^mf_{iq}$ and $\sigma_q$ The brave men, living and dead, who struggled, here, have consecrated it far above our poor power to add or detract. Suppose that
\[X_i=(x_{i1},\dots,x_{in}) \indent (i=1,\dots, m),\]  
where $x_{ij}=(f_{ij}-\overline{f}_j)/\sigma_j $ and
\[B=(X_1^T,\dots,X_m^T)^T.\]
 Then we can show that
 Our goal is to maximize this value under the constraint $a_1^Ta_1=1$. Let $\lambda_{\rm max}$ be the largest eigenvalue of
 $C$. According to the Rayleigh--Ritz theorem, $a_1$ can be obtained by solving
 \[Ca_1= \lambda_{\rm max}a_1.\]
But in a larger sense we can not dedicate -- we can not consecrate -- we can not hallow this ground. The brave men, living and dead, who struggled, here, have consecrated it far above our poor power to add or detract. The world will little note, nor long remember, what we say here, but can never forget what they did here. It is for us, the living, rather to be dedicated here to the unfinished work which they have, thus far, so nobly carried on \cite{abt1981}. It is rather for us to be here dedicated to the great task remaining before us  that from these honoured dead we take increased devotion to that cause for which they here gave the last full measure of devotion  that we here highly resolve that these dead shall not have died in vain; that this nation shall have a new birth of freedom; and that this government \cite{abt1984b} of the people, by the people, for the people, shall not perish from the earth.
\end{appendix}

\end{document}
